Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-04-03 Documents/Euler/Benchmarks1D/draft.tex
new figures for 11
changes to section 11 in document

\subsection{Test 11: Slow-moving Shock}
In this problem, a shock wave is present at about $x=0.5$.This test, like the previous one, shows significant oscilltions following the shock wave, particularly with higher order methods. However, these oscillations in the second and third order results appear to be more periodic than those in the previous test. 
\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T11.png} &
	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
	  \includegraphics[width=.4\textwidth]{vel_T11.png} &	
	  \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
      \includegraphics[width=.4\textwidth]{prs_T11.png} &	
      \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{Results for test 11 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line. Each pair of side-by-side panels shows the same results at different zoom levels. The top panels show density, the middle show velocity, and the bottom show pressure.}
\end{figure}

>>>>

\subsection{Test 11: Slow-moving Shock}
In this problem, a shock wave is present at about $x=0.5$.This test, like the previous one, shows significant oscilltions following the shock wave, particularly with higher order methods. However, these oscillations in the second and third order results appear to be more periodic than those in the previous test. 
\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T11.png} &
	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
	  \includegraphics[width=.4\textwidth]{vel_T11.png} &	
	  \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
      \includegraphics[width=.4\textwidth]{prs_T11.png} &	
      \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{Results for test 11 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line. Each pair of side-by-side panels shows the same results at different zoom levels. The top panels show density, the middle show velocity, and the bottom show pressure.}
\end{figure}
Subsequent runs of this test varied the values of $beta_TVB$ and $beta_TVD$, while maintaining the third order method. Lower values of $beta_TVB$ give more accurate results, with fewer, smaller oscillations appearing. Variations in $beta_TVD$ have some effect, but not a great one. A few of the oscillations appear larger with $beta_TVD$ set to 1.0, but the difference is not especially large.
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{11_300zoom.png}	
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{11_1zoom.png}
     \includegraphics[width=.475\textwidth]{11_2zoom.png}	
    \end{tabular}
  \end{center}
  \caption{Zoomed results for test 11 at $t=1$, computed with 400 cells and the third order method. The top panel shows results when $beta_TVB$ is set to 300, with varying values of $beta_TVD$: 1.0 (dotted blue), 1.5 (dashed green) and 2.0 (solid red). The bottom two panels show results when $beta_TVD$ is held constant, with varying values of $beta_TVB$: 0 (solid red), 10 (dashed green), 50 (dotted blue), and 300 (dash-dotted pink). $beta_TVD$ is set to 1.0 in the right panel and 2.0 in the left panel.}
\end{figure}
\clearpage
